The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-11 analysis/paper/paper.qmd
Update script for word counts

@@

# Read thesis metadata ----
data(emu_metadata)

# Load the raw text dataset 
data(emu_raw)

# Join  text with the metadata file  
emu <- left_join(emu_raw, emu_metadata, by = "ID")

@@

emu$text_clean <- emu$text_raw |>
  clean_basic()

@@

```{r top-words-document}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, top_n = 3)
```

@@

```{r}
# Preview term frequency distributions in a subset of theses
ggplot(emu_words_count |> 
         filter(title == unique(title)[1:6]),
       aes(n/total, fill = title)) +
  geom_histogram(show.legend = FALSE, binwidth = 0.0001) +
  xlim(NA, 0.0009) +
  facet_wrap(~ title, ncol = 3, scales = "free_y")
```

>>>>

# Read thesis metadata ----
data_path <- here("analysis", "data", "raw_data")
pdf_names <- dir(data_path, pattern = "*.pdf")

# TODO replace the following lines with the metadata included in the package
# emu_metadata <- data(emu_metadata)
## Read metadata for all theses
all_theses <- read_xlsx(path = here(data_path, "theses-all.xlsx"))

## Read only metadata for theses with PDF available
emu <- read_csv(here(data_path, "theses-metadata.csv")) |>
  mutate(text_raw = "") |>
  filter(!is.na(pdf_via))

# TODO replace this and next code chunk with reading `text_raw` from the package
# emu <- data(emu_raw)
pdf_paths <- here(data_path, emu$file_name)
```

@@

data_path <- here("analysis", "data", "derived_data", "emu_theses_with_text_and_location.csv")

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu$text_raw <- convert_pdf_text(pdf_paths)

  # Add latitude and longitude information to theses data frame
  emu <- geocode_thesis_locations(emu)

  # Write thesis dataframe to file
  write_csv(emu, data_path)
} else {
  emu$text_raw <- read_csv(data_path)$text
  emu$longitude <- read_csv(data_path)$longitude
  emu$latitude <- read_csv(data_path)$latitude
}

@@

emu$text_clean <- emu$text |>
  clean_basic()

@@

```{r top-words-document}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, top_n = 10)
```

@@

```{r}
# Preview term frequency distributions in a subset of theses

emu_words_count <- emu_words |> 
  count(title, word, sort = TRUE) |> 
  ungroup()

emu_words_total <- emu_words_count |> 
  group_by(title) |> 
  summarise(total = sum(n))

emu_words_count <- left_join(emu_words_count, emu_words_total)

ggplot(emu_words_count |> 
         filter(title == unique(title)[1:6]),
       aes(n/total, fill = title)) +
  geom_histogram(show.legend = FALSE, binwidth = 0.0001) +
  xlim(NA, 0.0009) +
  facet_wrap(~ title, ncol = 3, scales = "free_y")
```
